---
title: "Ch2.6 OCE of Kelley "
author: Taeyoon Song
date: February 24, 2020
output: 
  github_document:
    pandoc_args: --webtex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(oce)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## 2.6.1 sorting

sort()는 정열된 벡터를 반환, 반면 order()는 데이터의 인덱스를 정열될 순서로 나열:

```{r}
data(oceans, package="ocedata")
oceansOrdered <- oceans[order(oceans$AvgDepth),] # 컬럼기준 매트릭스 정열
oceans$rankByAvgDepth <- order(order(oceans$AvgDepth, decreasing = TRUE)) # Ranking 반환
```

## 2.6.2 해찾기

일변량 함수의 해는 `uniroot()`로 찾을 수 있음:
다항식 $a_1 + a_2x + a_3x^2$ 의 해찾기
```{r}
polyroot(c(-1, 0, 1))
```

## 2.6.3 적분
함수의 적분은 `integrate()`
$$\int_0^\pi \sin\theta\,d\theta$$
```{r}
integrate(sin, 0, pi)
woa <- function(x, a=1)
  8 * a^3 / (x^2 + 4*a^2)
integrate(woa, -Inf, Inf)

# Ex. 2.39
a <- 2
b <- 1
integrate(function(t)
  4*a*sqrt(1-(a^2-b^2)/a^2*sin(t)^2), 0, pi/2)
```

## 2.6.4 Piecewise Linear Interpolation
```{r}
data(ctd, package="oce")
p <- ctd[["pressure"]]
S <- ctd[["salinity"]]
Sinterp <- approx(p, S, seq(0, max(p), 0.5))$y
Sinterp
```


$$\epsilon = 15 \nu \int_0^\infty k^2 \phi \,dk$$

```{r}
data(turbulence, package="ocedata")
k <- turbulence$k
phi <- turbulence$phi
plot(k, k^2*phi, pch=20, ylim=c(0, 0.41),
     xlab=expression(k), ylab=expression(k^2*phi))
lfcn <- approxfun(k, k^2 * phi)
kk <- seq(min(k), max(k), length.out=100)
lines(kk, lfcn(kk))
I <- integrate(lfcn, min(k), max(k))
nu <- 1e4 * swViscosity(35, 10) / swRho(35, 10, 10, eos="unesco")
15 * nu * I$value

```


``
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
