---
title: "test for uploading into github"
author: Taeyoon Song
date: February 21, 2020
output: 
  github_document:
    toc: FALSE,
    toc_depth: 3,
    fig_width: 7,
    fig_height: 5,
    dev: "png",
    df_print: "default",
    includes: NULL,
    md_extensions: NULL,
    hard_line_breaks: TRUE,
    pandoc_args: NULL,
    html_preview: TRUE,
    keep_html: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
